MSAD_PCA_Walkthrough

### 2017-01-24 Simulation_Vignette.Rmd
Added alarm codes to check method-specific false alarm rates: 1 = T2, 2 = SPE, 3 = Both. At three flags to trigger and alpha = 0.001, SPE throws no false alarms in 1440 rows and T2 throws 1. However, SPE throws no false alarms even when alpha is as large as 0.07, while for this alpha the T2 false alarm rate is nearly 16 percent.

falseAlarmRate_SPE <- sum(results_ls$Alarms[,1] == "Alarm") /
  nrow(results_ls$Alarms)
falseAlarmRate_T2 <- sum(results_ls$Alarms[,2] == "Alarm") /
  nrow(results_ls$Alarms)

faultTime <- zoo::index(faults_ls$normal[faultStart,])
# Why don't we have 10080 - 2880 rows in the Alarm matrix??
str(results_ls$Alarms)

```

>>>>

# Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
falseAlarmRate_SPE <- sum(results_ls$FaultChecks[,5] %in% c(2,3)) /
  nrow(results_ls$FaultChecks)
# The SPE false alarm rate hits 0 at alpha = 0.07.
falseAlarmRate_T2 <- sum(results_ls$FaultChecks[,5] %in% c(1,3)) /
  nrow(results_ls$FaultChecks)
# The T2 false alarm rate hits 0 at alpha = 0.00015, and is at 16% at 0.07. The
# T2 statistic throws too many false alarms for my taste.

# Why don't we have 10080 - 2880 rows in the Alarm matrix?? We need to set the
# simulation run so that this mspMonitor function crawls over all 10080 rows.
# Right now, the code does not "learn" after each run. At each updateFreq, we
# need the function to append the non-alarmed test data to the training data,
# and then rerun mspMonitor on the next updateFreq observations.
```
